---
title: "Visualizing Survival ML Performance"
author: "Lathan Liou"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
      keep_md: true
      toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(readxl)
library(fs)
library(cowplot)
library(ggridges)
library(forcats)
library(patchwork)
library(DT)
library(kableExtra)
all_files <- list.files(path = "results",
                        full.names = TRUE,
                        pattern = "*.csv")
all_res <- all_files %>%
  map(~read_csv(.) %>%
        janitor::clean_names()) %>%
  setNames(all_files %>% 
             str_replace(".csv", "") %>%
             str_replace("results/", ""))

#recode random forest output variables to match order
all_res[[21]]$x1 <- str_replace_all(all_res[[22]]$x1, "\\.", "") 
all_res[[22]]$x1 <- str_replace_all(all_res[[22]]$x1, "\\.", "") 
all_res[[21]] <- all_res[[21]][match(all_res[[2]]$x1, all_res[[21]]$x1),]
all_res[[22]] <- all_res[[22]][match(all_res[[3]]$x1, all_res[[22]]$x1),]

# modify rfsrc df to fit the others, since I had to use a reduced input set of vars
# full_vars = data.frame(variable = all_res$cox_1_featsel_$variable)
# new_rfsrc_featsel <- left_join(full_vars, all_res$rfsrc_1_featsel_,
#                                by = "variable")
# all_res$rfsrc_1_featsel_ <- new_rfsrc_featsel
elizabeth_vars <- read_excel("data/elizabeth_vars.xlsx",
                             sheet = 3) %>%
  select(1:4)
```

## Comparing Short-Term and Long-Term C-Index
We may observe a higher C-index in shorter time-to-event cases. To roughly see this, we compare the cross-validated C-index of an SRTR cohort including patients who received transplants on an index date of 1-1-2011 with unaltered follow-up time with that of the same cohort of patients artificially censored after 2 years of follow-up.

```{r, warning=FALSE, message=FALSE, eval=FALSE}
make_perf_df <- function(start) {
  # retrieve all perf indices
  ind <- str_which(names(start), "_perf_")
  ci_wide <- map_dfc(ind, function(ind) start %>% pluck(ind) %>% select(-variable))
  ci_long <- ci_wide %>%
    pivot_longer(everything(),
                 names_to = "model",
                 values_to = "cindex")
  ci_long
}

test_files <- list.files(path = "results_test",
                         full.names = TRUE,
                         pattern = "*.csv")
test_res <- test_files %>%
  map(~read_csv(.) %>%
        janitor::clean_names()) %>%
  setNames(test_files %>% 
             str_replace(".csv", "") %>%
             str_replace("results_test/", ""))

make_perf_df(test_res) %>%
  mutate(model = case_when(
    model == "cox_ph_scale...1" ~ "Long-Term",
    model == "cox_ph_scale...2" ~ "Short-Term"
  )) %>%
  group_by(model) %>%
  dplyr::summarize(mean_cindex = mean(cindex, na.rm = TRUE),
                   sd_cindex = sd(cindex, na.rm = TRUE),
                   lb_cindex = quantile(cindex, probs = 0.025, na.rm = TRUE),
                   ub_cindex = quantile(cindex, probs = 0.975, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(mean_cindex))
```

## C-indices

```{r prep_perf_df}
make_perf_df <- function(start) {
  # retrieve all perf indices
  ind <- str_which(names(start), "_perf_")
  ci_wide <- map_dfc(ind, function(ind) all_res %>% pluck(ind) %>% select(-x1))
  ci_long <- ci_wide %>%
    pivot_longer(everything(),
                 names_to = "model",
                 values_to = "cindex")
  ci_long
}
perf_df <- make_perf_df(all_res)
perf_df$model <- recode(perf_df$model,
                        rfsrc_scale = "Random Survival Forests",
                        xgb_tree_tuned = "XGBoost Tree",
                        ridge = "Ridge",
                        cox_boost_tuned = "Cox Boost",
                        xgb_linear = "XGBoost Linear",
                        elastic_net = "Elastic Net",
                        lasso = "Lasso",
                        cox_ph = "CoxPH")
```

## T-test on C-indices
Using as reference: https://medium.com/analytics-vidhya/using-the-corrected-paired-students-t-test-for-comparing-the-performance-of-machine-learning-dc6529eaa97f

Nadeau and Bengio

```{r}
library(correctR)
ind <- str_which(names(all_res), "_perf_")
ci_wide <- map_dfc(ind, function(ind) all_res %>% pluck(ind) %>% select(-x1)) %>%
  mutate(k = as.numeric(rep(1:5, each = 5)),
         r = as.numeric(rep(1:5, 5)))
ci_long <- ci_wide %>%
  pivot_longer(cox_ph:xgb_tree_tuned,
               names_to = "model",
               values_to = "values")

expand.grid.unique <- function(x, y, include.equals=FALSE)
{
  x <- unique(x)
  
  y <- unique(y)
  
  g <- function(i)
  {
    z <- setdiff(y, x[seq_len(i-include.equals)])
    
    if(length(z)) cbind(x[i], z, deparse.level=0)
  }
  
  do.call(rbind, lapply(seq_along(x), g))
}

pairs <- expand.grid.unique(unique(ci_long$model),
                            unique(ci_long$model)) %>% 
  as.data.frame()

pvalues <- map2(pairs$V1, pairs$V2,
                ~ repkfold_ttest(data = ci_long %>%
                                   filter(model %in% c(.x, .y)) %>%
                                   select(model, values, k, r) %>%
                                   mutate(model = as.numeric(case_when(
                                     model == .x ~ 1,
                                     TRUE ~ 2
                                   ))) %>%
                                   as.data.frame(),
                                 n1 = 5156,
                                 n2 = 1288,
                                 k = 5,
                                 r = 5)) %>%
  purrr::list_rbind()

pval_df <- cbind(pairs, pvalues) %>% 
  as.data.frame() %>%
  dplyr::mutate(statistic = round(statistic, digits = 2),
                adj_pval = scales::pvalue(p.adjust(p.value, method = "bonferroni")),
                p.value = scales::pvalue(p.value))
pval_df %>%
  kbl() %>%
  kable_styling()
```

### Table
```{r perf_tbl}
perf_df %>%
  group_by(model) %>%
  dplyr::summarize(mean_cindex = mean(cindex, na.rm = TRUE),
                   sd_cindex = sd(cindex, na.rm = TRUE),
                   lb_cindex = quantile(cindex, probs = 0.025, na.rm = TRUE),
                   ub_cindex = quantile(cindex, probs = 0.975, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(mean_cindex)) %>%
  kbl() %>%
  kable_styling()
```

### Violin Plot
```{r model_comp_violin}
perf_df %>%
  mutate(model = fct_relevel(model,
                             "CoxPH",
                             "Ridge",
                             "Lasso",
                             "Elastic Net",
                             "Cox Boost",
                             "XGBoost Linear",
                             "XGBoost Tree",
                             "Random Survival Forests")) %>%
  ggplot(aes(x = model, y = cindex, fill = model)) + 
  geom_violin(alpha = 0.5) +
  geom_point(alpha = 0.5) +
  stat_summary(fun = "mean",
               geom = "crossbar", 
               width = 0.3,
               colour = "black") +
  theme_bw() +
  labs(x = "Model",
       y = "C-index",
       fill = "Model") + 
  coord_flip() + 
  scale_x_discrete(limits = rev) +
  annotate("rect", xmin = 4.5, xmax = 7.5,
           ymin = 0.69, ymax = 0.7) +
  annotate("text",
           x = 6,
           y = 0.695,
           col = "white",
           label = "Penalized",
           angle = 90) +
  annotate("rect", xmin = 1.7, xmax = 4.3,
           ymin = 0.69, ymax = 0.7) +
  annotate("text",
           x = 3,
           y = 0.695,
           col = "white",
           label = "Boost",
           angle = 90) +
  annotate("rect", xmin = 0.5, xmax = 1.5,
           ymin = 0.69, ymax = 0.7) +
  annotate("text",
           x = 1,
           y = 0.695,
           col = "white",
           label = "Tree",
           angle = 90)

```

## Features

### Selected Features Heatmap {.tabset}

```{r}
get_feat_selections <- function(start) {
  ind <- str_which(names(start), "_featsel_(?!aggr_)")
  feat_wide <- map_dfc(ind, ~ all_res %>% 
                         pluck(.x) %>% 
                         pivot_longer(-any_of(c("x1", "total")),
                                      names_to = "iter",
                                      values_to = "weight") %>%
                         group_by(x1) %>%
                         dplyr::summarize("{names(all_res)[[.x]]}" := sum(weight != 0, na.rm = TRUE)) %>%
                         ungroup() %>%
                         column_to_rownames(var = "x1"))
  feat_long <- feat_wide %>%
    rownames_to_column(var = "variable") %>%
    pivot_longer(-variable,
                 names_to = "model",
                 values_to = "n_selections")
  feat_long
}

feat_selections <- get_feat_selections(all_res)

plot_featsel_heatmap <- function(vars) {
  feat_selections %>%
    mutate(model = case_when(
      model == "cox_1_featsel_" ~ "Cox",
      model == "eln_1_featsel_" ~ "Elastic Net",
      model == "gbmboost_1_featsel_" ~ "Cox Boost",
      model == "lasso_1_featsel_" ~ "Lasso",
      model == "rfsrc_1_featsel_" ~ "Random Survival Forests",
      model == "ridge_1_featsel_" ~ "Ridge",
      model == "xgbl_1_featsel_" ~ "XGBoost Linear",
      model == "xgbt_1_featsel_" ~ "XGBoost Tree"
    )) %>%
    filter(!model %in% c("Random Survival Forests", "Ridge", "XGBoost Linear"),
           str_detect(variable, paste(vars, collapse = "|"))) %>%
    ggplot(aes(x = model, y = variable, fill = n_selections)) +
    geom_tile() + 
    geom_text(aes(label = n_selections), col = "black", size = 6) +
    scale_fill_gradient(low = "white", high = "blue") + 
    theme_bw() +
    labs(x = "Model",
         y = "Variable",
         fill = "Number of\nSelections") + 
    scale_y_discrete(limits = rev)
}

dem_vars <- elizabeth_vars %>%
  filter(status %in% c("demographic", "clinical")) %>%
  pull(variable)

rec_vars <- elizabeth_vars %>%
  filter(status == "recipient") %>%
  pull(variable)

can_vars <- elizabeth_vars %>% 
  filter(status == "candidate") %>% 
  pull(variable)

don_vars <- elizabeth_vars %>% 
  filter(status == "donor") %>% 
  pull(variable)

proc_vars <- elizabeth_vars %>%
  filter(status == "procedural") %>% 
  pull(variable)
```

#### Demographic and Clinical

```{r featsel_heatmap_dem, include = TRUE, fig.width = 8, fig.height = 12}
plot_featsel_heatmap(dem_vars)
```

#### Recipient
```{r featsel_heatmap_rec, include = TRUE, fig.width = 8, fig.height = 12}
plot_featsel_heatmap(rec_vars)
```

#### Candidate
```{r featsel_heatmap_can, include = TRUE, fig.width = 8, fig.height = 12}
plot_featsel_heatmap(can_vars)
```

#### Donor
```{r featsel_heatmap_don, include = TRUE, fig.width = 8, fig.height = 12}
plot_featsel_heatmap(don_vars)
```

#### Procedural
```{r featsel_heatmap_proc, include = TRUE, fig.width = 8, fig.height = 12}
plot_featsel_heatmap(proc_vars)
```

### Selected Features {.tabset}
```{r}
# filter out variables that were never selected by any method, excluding ridge
feat_sel_stats <- feat_selections %>%
  filter(!str_detect(model, "ridge")) %>%
  group_by(variable) %>%
  dplyr::summarize(avg_times = mean(n_selections, na.rm = TRUE),
                   tot_times = sum(n_selections, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(avg_times))
```

A selection of a feature is related to how important a model deemed it

#### All
```{r top_20_feat}
feat_sel_stats %>%
  slice(1:20) %>% 
  mutate(avg_times = round(avg_times, 1),
         variable = recode(variable,
                           REC_AGE_AT_TX = "Age at Transplant",
                           REC_TOT_BILI = "Bilirubin",
                           bmi_calculated = "BMI",
                           REC_HR_ISCH = "Total Ischemic Time (min.)",
                           DON_AGE = "Donor Age",
                           CARDIAC_ETIOLOGY3 = "Ischemic Cardiomyopathy",
                           CARDIAC_ETIOLOGY2 = "Dilated Cardiomyopathy",
                           WAIT_TIME = "Time on Waitlist",
                           status_change = "Change in Priority Status",
                           REC_HBV_ANTIBODY0 = "HBV Negative",
                           DM_Baseline = "Diabetes",
                           INSURANCE1 = "Medicaid",
                           REC_CARDIAC_SURG = "Prior Cardiac Surgery",
                           VAD = "VAD",
                           REC_CREAT = "Creatinine (mg/dL) Prior to Transplant",
                           XCAN_FUNCTIONAL_STATUS3 = "Normal Functional Status",
                           REC_TXFUS = "Received Prior Transfusion",
                           PREV_MALIG = "Previous Malignancies",
                           XCAN_EDUCATION2 = "High School Education",
                           Dialysis_Baseline = "Prior Dialysis",
                           PVR = "Pre-Transplant Pulmonary Vascular Resistance",
                           MDRDeGFR_B = "eGFR",
                           REC_CMV_STAT0 = "CMV Negative",
                           REC_ECMO = "ECMO",
                           MDRDeGFR_WL = "Waitlist eGFR",
                           REC_HLA_TYP_DONE = "HLA Typing Performed",
                           REC_EBV_STAT0 = "EBV Negative",
                           REC_PROCEDURE_TY_HR2 = "Orthotopic Traditional Procedure",
                           CARDIAC_ETIOLOGY6 = "Idiopathic Cardiac Etiology",
                           REC_IABP = "Bridged with IABP")) %>%
  ggplot(aes(x = forcats::fct_reorder(variable, avg_times),
             y = avg_times)) + 
  geom_col() +
  geom_text(aes(label = avg_times), hjust = 1, col = "white") +
  coord_flip() + 
  theme_bw() + 
  labs(x = "Variable",
       y = "Average number of times selected across all models")
```

```{r top_20_feat_indiv}
get_feat_sel_by_model <- function(feat_sel,
                                  .model,
                                  plot_title) {
  var_df <- feat_sel %>%
    filter(!str_detect(model, "cox"),
           !str_detect(model, "ridge"),
           str_detect(model, .model)) %>%
    arrange(desc(n_selections))
  
  ggplot(var_df %>%
           slice(1:20),
         aes(x = forcats::fct_reorder(variable, n_selections),
             y = n_selections)) + 
    geom_col() +
    coord_flip() + 
    theme_bw() + 
    labs(x = "Variable",
         y = "Number of times selected",
         title = plot_title)
}
feat_sel_tibble <- tibble(model_regex = c("lasso",
                                          "eln",
                                          "gbmboost"),
                          model = c("Lasso",
                                    "Elastic Net",
                                    "Cox Boost"))
individual_featsel_plots <- map2(feat_sel_tibble$model_regex,
                                 feat_sel_tibble$model,
                                 ~get_feat_sel_by_model(feat_selections,
                                                        .x, .y))
```

#### Lasso
```{r featsel_lasso}
p1 <- individual_featsel_plots[[1]] +
  geom_text(aes(label = n_selections), hjust = 1, col = "white")
p1
```

#### Elastic Net
```{r featsel_eln}
p2 <- individual_featsel_plots[[2]] +
  geom_text(aes(label = n_selections), hjust = 1, col = "white") 
p2
```

#### Cox Boost
```{r featsel_boost}
p3 <- individual_featsel_plots[[3]] + 
  geom_text(aes(label = n_selections), hjust = 1, col = "white")
p3
```

#### Cowplot of Feature Selection
```{r grid_featsel, include = TRUE, fig.width = 10, fig.height = 9}
(p1 + p2) / (p3 + plot_spacer())
```

### Direction of features {.tabset}

```{r}
get_feat_magnitude <- function(start) {
  ind <- str_which(names(start), "_featsel_(?!aggr_)")
  feat_wide <- map(ind, ~ all_res %>% 
                     pluck(.x) %>% 
                     select(-any_of("total")) %>%
                     pivot_longer(-x1,
                                  names_to = "iter",
                                  values_to = "weight") %>%
                     select(-iter) %>%
                     mutate(id = row_number()) %>%
                     rename("{names(all_res)[[.x]]}" := "weight")) %>%
    reduce(left_join, by = c("x1",
                             "id")) %>%
    rename(variable = x1)
}

ind <- str_which(names(all_res), "rfsrc_1_featsel_(?!aggr_)")

feat_magnitude <- get_feat_magnitude(all_res)

feat_magnitude_long <- feat_magnitude %>%
  pivot_longer(-c(variable, id),
               names_to = "method",
               values_to = "weight") %>%
  mutate(method = str_replace(method, "_1_featsel_", ""))

create_weight_table <- function(.method,
                                vars) {
  if(.method %in% c("ridge", "lasso", "eln")) {
    feat_magnitude_long %>%
    filter(method == .method,
           weight != 0,
           str_detect(variable, paste(vars, collapse = "|"))) %>% 
    group_by(method, variable) %>%
    mutate(hr = exp(weight)) %>%
    summarize(mean_hr = mean(hr, na.rm = TRUE),
              sd_hr = sd(hr, na.rm = TRUE),
              median_hr = median(hr, na.rm = TRUE),
              iqr_hr = IQR(hr, na.rm = TRUE),
              lb = quantile(hr, 0.025),
              ub = quantile(hr, 0.975)) %>%
    ungroup() %>%
    mutate(across(mean_hr:iqr_hr, round, 3))
  } else {
    feat_magnitude_long %>%
      filter(method == .method,
             weight != 0,
             str_detect(variable, paste(vars, collapse = "|"))) %>% 
      group_by(method, variable) %>%
      summarize(mean_weight = mean(weight, na.rm = TRUE),
                sd_weight = sd(weight, na.rm = TRUE),
                median_weight = median(weight, na.rm = TRUE),
                iqr_weight = IQR(weight, na.rm = TRUE),
                lb = quantile(weight, 0.025),
                ub = quantile(weight, 0.975)) %>%
      ungroup() %>%
      mutate(across(mean_weight:iqr_weight, round, 3))
  }
}

create_weight_boxplot <- function(.method,
                                  vars) {
  if(.method %in% c("ridge", "lasso", "eln")) {
    feat_magnitude_long %>%
      filter(method == .method,
             str_detect(variable, paste(vars, collapse = "|"))) %>% 
      mutate(hr = exp(weight)) %>%
      ggplot(aes(x = forcats::fct_reorder(variable, hr), y = hr, color = variable)) +
      geom_boxplot() +
      geom_hline(yintercept = 1,
                 alpha = 0.3) +
      theme_bw() +
      coord_flip() +
      labs(x = "Variable",
           y = "Hazard Ratio") + 
      theme(legend.position = "none")
  } else {
    feat_magnitude_long %>%
      filter(method == .method,
             str_detect(variable, paste(vars, collapse = "|"))) %>% 
      ggplot(aes(x = forcats::fct_reorder(variable, weight), y = weight, color = variable)) +
      geom_boxplot() +
      theme_bw() +
      coord_flip() +
      labs(x = "Variable",
           y = "Importance") + 
      theme(legend.position = "none")
  }
}
```

#### Ridge

##### Demographic and Clinical

```{r weights_ridge_dem, include = TRUE}
create_weight_boxplot("ridge", dem_vars)
```

##### Recipient
```{r weights_ridge_rec, include = TRUE}
create_weight_boxplot("ridge", rec_vars)
```

##### Candidate
```{r weights_ridge_can, include = TRUE}
create_weight_boxplot("ridge", can_vars)
```

##### Donor
```{r weights_ridge_don, include = TRUE}
create_weight_boxplot("ridge", don_vars)
```

##### Procedural
```{r weights_ridge_proc, include = TRUE}
create_weight_boxplot("ridge", proc_vars)
```

#### Lasso

##### Demographic and Clinical
```{r weights_lasso_dem, include = TRUE}
create_weight_boxplot("lasso", dem_vars)
```

##### Recipient
```{r weights_lasso_rec, include = TRUE}
create_weight_boxplot("lasso", rec_vars)
```

##### Candidate
```{r weights_lasso_can, include = TRUE}
create_weight_boxplot("lasso", can_vars)
```

##### Donor
```{r weights_lasso_don, include = TRUE}
create_weight_boxplot("lasso", don_vars)
```

##### Procedural
```{r weights_lasso_proc, include = TRUE}
create_weight_boxplot("lasso", proc_vars)
```

#### Elastic Net

##### Demographic and Clinical
```{r weights_eln_dem, include = TRUE}
create_weight_boxplot("eln", dem_vars)
```

##### Recipient
```{r weights_eln_rec, include = TRUE}
create_weight_boxplot("eln", rec_vars)
```

##### Candidate
```{r weights_eln_can, include = TRUE}
create_weight_boxplot("eln", can_vars)
```

##### Donor
```{r weights_eln_don, include = TRUE}
create_weight_boxplot("eln", don_vars)
```

##### Procedural
```{r weights_eln_proc, include = TRUE}
create_weight_boxplot("eln", proc_vars)
```

#### Cox Boost

##### Demographic and Clinical
```{r weights_boost_dem, include = TRUE}
create_weight_boxplot("gbmboost", dem_vars)
```

##### Recipient
```{r weights_boost_rec, include = TRUE}
create_weight_boxplot("gbmboost", rec_vars)
```

##### Candidate
```{r weights_boost_can, include = TRUE}
create_weight_boxplot("gbmboost", can_vars)
```

##### Donor
```{r weights_boost_don, include = TRUE}
create_weight_boxplot("gbmboost", don_vars)
```

##### Procedural
```{r weights_boost_proc, include = TRUE}
create_weight_boxplot("gbmboost", proc_vars)
```

#### XGBL

##### Demographic and Clinical
```{r weights_xgbl_dem, include = TRUE}
create_weight_boxplot("xgbl", dem_vars)
```

##### Recipient
```{r weights_xgbl_rec, include = TRUE}
create_weight_boxplot("xgbl", rec_vars)
```

##### Candidate
```{r weights_xgbl_can, include = TRUE}
create_weight_boxplot("xgbl", can_vars)
```

##### Donor
```{r weights_xgbl_don, include = TRUE}
create_weight_boxplot("xgbl", don_vars)
```

##### Procedural
```{r weights_xgbl_proc, include = TRUE}
create_weight_boxplot("xgbl", proc_vars)
```

#### XGBoost Tree

##### Demographic and Clinical
```{r weights_xbgt_dem, include = TRUE}
create_weight_boxplot("xgbt", dem_vars)
```

##### Recipient
```{r weights_xgbt_rec, include = TRUE}
create_weight_boxplot("xgbt", rec_vars)
```

##### Candidate
```{r weights_xgbt_can, include = TRUE}
create_weight_boxplot("xgbt", can_vars)
```

##### Donor
```{r weights_xgbt_don, include = TRUE}
create_weight_boxplot("xgbt", don_vars)
```

##### Procedural
```{r weights_xgbt_proc, include = TRUE}
create_weight_boxplot("xgbt", proc_vars)
```

#### RFSRC

##### Demographic and Clinical
```{r weights_rfsrc_dem, include = TRUE}
create_weight_boxplot("rfsrc", dem_vars)
```

##### Recipient
```{r weights_rfsrc_rec, include = TRUE}
create_weight_boxplot("rfsrc", rec_vars)
```

##### Candidate
```{r weights_rfsrc_can, include = TRUE}
create_weight_boxplot("rfsrc", can_vars)
```

##### Donor
```{r weights_rfsrc_don, include = TRUE}
create_weight_boxplot("rfsrc", don_vars)
```

##### Procedural
```{r weights_rfsrc_proc, include = TRUE}
create_weight_boxplot("rfsrc", proc_vars)
```

### Significant Features Only {.tabset}
#### Ridge

##### Demographic and Clinical
```{r weights_ridge_dem_tbl, include = TRUE}
ridge_weight_dem <- create_weight_table("ridge", dem_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
ridge_weight_dem %>%
  kbl() %>%
  kable_styling()
```

##### Recipient
```{r weights_ridge_rec_tbl, include = TRUE}
ridge_weight_rec <- create_weight_table("ridge", rec_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
ridge_weight_rec %>%
  kbl() %>%
  kable_styling()
```

##### Candidate
```{r weights_ridge_can_tbl, include = TRUE}
ridge_weight_can <- create_weight_table("ridge", can_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
ridge_weight_can %>%
  kbl() %>%
  kable_styling()
```

##### Donor
```{r weights_ridge_don_tbl, include = TRUE}
ridge_weight_don <- create_weight_table("ridge", don_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
ridge_weight_don %>%
  kbl() %>%
  kable_styling()
```

##### Procedural
```{r weights_ridge_proc_tbl, include = TRUE}
ridge_weight_proc <- create_weight_table("ridge", proc_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
ridge_weight_proc %>%
  kbl() %>%
  kable_styling()
```

#### Lasso

##### Demographic and Clinical
```{r weights_lasso_dem_tbl, include = TRUE}
lasso_weight_dem <- create_weight_table("lasso", dem_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
lasso_weight_dem %>%
  kbl() %>%
  kable_styling()
```

##### Recipient
```{r weights_lasso_rec_tbl, include = TRUE}
lasso_weight_rec <- create_weight_table("lasso", rec_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
lasso_weight_rec %>%
  kbl() %>%
  kable_styling()
```

##### Candidate
```{r weights_lasso_can_tbl, include = TRUE}
lasso_weight_can <- create_weight_table("lasso", can_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
lasso_weight_can %>%
  kbl() %>%
  kable_styling()
```

##### Donor
```{r weights_lasso_don_tbl, include = TRUE}
lasso_weight_don <- create_weight_table("lasso", don_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
lasso_weight_don %>%
  kbl() %>%
  kable_styling()
```

##### Procedural
```{r weights_lasso_proc_tbl, include = TRUE}
lasso_weight_proc <- create_weight_table("lasso", proc_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
lasso_weight_proc %>%
  kbl() %>%
  kable_styling()
```

#### Elastic Net

##### Demographic and Clinical
```{r weights_eln_dem_tbl, include = TRUE}
eln_weight_dem <- create_weight_table("eln", dem_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
eln_weight_dem %>%
  kbl() %>%
  kable_styling()
```

##### Recipient
```{r weights_eln_rec_tbl, include = TRUE}
eln_weight_rec <- create_weight_table("eln", rec_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
eln_weight_rec %>%
  kbl() %>%
  kable_styling()
```

##### Candidate
```{r weights_eln_can_tbl, include = TRUE}
eln_weight_can <- create_weight_table("eln", can_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
eln_weight_can %>%
  kbl() %>%
  kable_styling()
```

##### Donor
```{r weights_eln_don_tbl, include = TRUE}
eln_weight_don <- create_weight_table("eln", don_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
eln_weight_don %>%
  kbl() %>%
  kable_styling()
```

##### Procedural
```{r weights_eln_proc_tbl, include = TRUE}
eln_weight_proc <- create_weight_table("eln", proc_vars) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
eln_weight_proc %>%
  kbl() %>%
  kable_styling()
```

#### Cox Boost

##### All
```{r boost_top}
create_weight_table("gbmboost", elizabeth_vars$variable) %>%
  filter(lb > 0 | ub < 0) %>%
  arrange(desc(mean_weight)) %>%
  slice_head(n = 20) %>%
  ggplot(aes(x = forcats::fct_reorder(variable, mean_weight),
             y = mean_weight, fill = variable)) + 
  geom_col() +
  theme_bw() +
  theme(legend.position = "none") +
  labs(x = "Significant Predictor Variables", 
       y = "Average Importance") +
  coord_flip()
```

##### Demographic and Clinical
```{r weights_boost_dem_tbl, include = TRUE}
gbm_weight_dem <- create_weight_table("gbmboost", dem_vars) %>%
  filter(lb > 0 | ub < 0) 
gbm_weight_dem %>%
  kbl() %>%
  kable_styling()
```

##### Recipient
```{r weights_boost_rec_tbl, include = TRUE}
gbm_weight_rec <- create_weight_table("gbmboost", rec_vars) %>%
  filter(lb > 0 | ub < 0) 
gbm_weight_rec %>%
  kbl() %>%
  kable_styling()
```

##### Candidate
```{r weights_boost_can_tbl, include = TRUE}
gbm_weight_can <- create_weight_table("gbmboost", can_vars) %>%
  filter(lb > 0 | ub < 0) 
gbm_weight_can %>%
  kbl() %>%
  kable_styling()
```

##### Donor
```{r weights_boost_don_tbl, include = TRUE}
gbm_weight_don <- create_weight_table("gbmboost", don_vars) %>%
  filter(lb > 0 | ub < 0) 
gbm_weight_don %>%
  kbl() %>%
  kable_styling()
```

##### Procedural
```{r weights_boost_proc_tbl, include = TRUE}
gbm_weight_proc <- create_weight_table("gbmboost", proc_vars) %>%
  filter(lb > 0 | ub < 0) 
gbm_weight_proc %>%
  kbl() %>%
  kable_styling()
```

#### XGBL

##### Demographic and Clinical
```{r weights_xgbl_dem_tbl, include = TRUE}
xgbl_weight_dem <- create_weight_table("xgbl", dem_vars) %>%
  filter(lb > 0 | ub < 0) 
xgbl_weight_dem %>%
  kbl() %>%
  kable_styling()
```

##### Recipient
```{r weights_xgbl_rec_tbl, include = TRUE}
xgbl_weight_rec <- create_weight_table("xgbl", rec_vars) %>%
  filter(lb > 0 | ub < 0) 
xgbl_weight_rec %>%
  kbl() %>%
  kable_styling()
```

##### Candidate
```{r weights_xgbl_can_tbl, include = TRUE}
xgbl_weight_can <- create_weight_table("xgbl", can_vars) %>%
  filter(lb > 0 | ub < 0) 
xgbl_weight_can %>%
  kbl() %>%
  kable_styling()
```

##### Donor
```{r weights_xgbl_don_tbl, include = TRUE}
xgbl_weight_don <- create_weight_table("xgbl", don_vars) %>%
  filter(lb > 0 | ub < 0) 
xgbl_weight_don %>%
  kbl() %>%
  kable_styling()
```

##### Procedural
```{r weights_xgbl_proc_tbl, include = TRUE}
xgbl_weight_proc <- create_weight_table("xgbl", proc_vars) %>%
  filter(lb > 0 | ub < 0) 
xgbl_weight_proc %>%
  kbl() %>%
  kable_styling()
```

#### XGBoost Tree

##### All
```{r xgbt_top}
create_weight_table("xgbt", elizabeth_vars$variable) %>%
  filter(lb > 0 | ub < 0) %>%
  arrange(desc(mean_weight)) %>%
  slice_head(n = 20) %>%
  ggplot(aes(x = forcats::fct_reorder(variable, mean_weight),
             y = mean_weight, fill = variable)) + 
  geom_col() +
  theme_bw() +
  theme(legend.position = "none") +
  labs(x = "Significant Predictor Variables", 
       y = "Average Importance") +
  coord_flip()
```

##### Demographic and Clinical
```{r weights_xbgt_dem_tbl, include = TRUE}
xgbt_weight_dem <- create_weight_table("xgbt", dem_vars) %>%
  filter(lb > 0 | ub < 0) 
xgbl_weight_dem %>%
  kbl() %>%
  kable_styling()
```

##### Recipient
```{r weights_xgbt_rec_tbl, include = TRUE}
xgbt_weight_rec <- create_weight_table("xgbt", rec_vars) %>%
  filter(lb > 0 | ub < 0) 
xgbl_weight_rec %>%
  kbl() %>%
  kable_styling()
```

##### Candidate
```{r weights_xgbt_can_tbl, include = TRUE}
xgbt_weight_can <- create_weight_table("xgbt", can_vars) %>%
  filter(lb > 0 | ub < 0) 
xgbl_weight_can %>%
  kbl() %>%
  kable_styling()
```

##### Donor
```{r weights_xgbt_don_tbl, include = TRUE}
xgbt_weight_don <- create_weight_table("xgbt", don_vars) %>%
  filter(lb > 0 | ub < 0) 
xgbl_weight_don %>%
  kbl() %>%
  kable_styling()
```

##### Procedural
```{r weights_xgbt_proc_tbl, include = TRUE}
xgbt_weight_proc <- create_weight_table("xgbt", proc_vars) %>%
  filter(lb > 0 | ub < 0) 
xgbl_weight_proc %>%
  kbl() %>%
  kable_styling()
```

#### RFSRC

##### All
```{r rfsrc_top}
create_weight_table("rfsrc", elizabeth_vars$variable) %>%
  filter(lb > 0 | ub < 0) %>%
  arrange(desc(mean_weight)) %>%
  slice_head(n = 20) %>%
  ggplot(aes(x = forcats::fct_reorder(variable, mean_weight),
             y = mean_weight, fill = variable)) + 
  geom_col() +
  theme_bw() +
  theme(legend.position = "none") +
  labs(x = "Significant Predictor Variables", 
       y = "Average Importance") +
  coord_flip()
```

##### Demographic and Clinical
```{r weights_rfsrc_dem_tbl, include = TRUE}
rfsrc_weight_dem <- create_weight_table("rfsrc", dem_vars) %>%
  filter(lb > 0 | ub < 0) 
rfsrc_weight_dem %>%
  kbl() %>%
  kable_styling()
```

##### Recipient
```{r weights_rfsrc_rec_tbl, include = TRUE}
rfsrc_weight_rec <- create_weight_table("rfsrc", rec_vars) %>%
  filter(lb > 0 | ub < 0) 
rfsrc_weight_rec %>%
  kbl() %>%
  kable_styling()
```

##### Candidate
```{r weights_rfsrc_can_tbl, include = TRUE}
rfsrc_weight_can <- create_weight_table("rfsrc", can_vars) %>%
  filter(lb > 0 | ub < 0) 
rfsrc_weight_can %>%
  kbl() %>%
  kable_styling()
```

##### Donor
```{r weights_rfsrc_don_tbl, include = TRUE}
rfsrc_weight_don <- create_weight_table("rfsrc", don_vars) %>%
  filter(lb > 0 | ub < 0) 
rfsrc_weight_don %>%
  kbl() %>%
  kable_styling()
```

##### Procedural
```{r weights_rfsrc_proc_tbl, include = TRUE}
rfsrc_weight_proc <- create_weight_table("rfsrc", proc_vars) %>%
  filter(lb > 0 | ub < 0) 
rfsrc_weight_proc %>%
  kbl() %>%
  kable_styling()
```

### Shared Across Ridge, Lasso, ELN {.tabset}

#### Top 20 Strongest Overall
```{r}
all_ridge <- create_weight_table("ridge", elizabeth_vars$variable) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
all_lasso <- create_weight_table("lasso", elizabeth_vars$variable) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 
all_eln <- create_weight_table("eln", elizabeth_vars$variable) %>%
  filter(abs(lb) > 1,
         abs(ub) > 1) 

shared_vars <- Reduce(intersect, list(all_ridge$variable,
                                      all_lasso$variable,
                                      all_eln$variable))
  
common_ridge <- all_ridge %>%
  filter(variable %in% shared_vars)
common_lasso <- all_ridge %>%
  filter(variable %in% shared_vars)
common_eln <- all_ridge %>%
  filter(variable %in% shared_vars)
  
tibble(variable = common_ridge$variable,
       shared_mean_hr = rowMeans(cbind(common_ridge$mean_hr,
                                       common_lasso$mean_hr,
                                       common_eln$mean_hr)),
       shared_lb = rowMeans(cbind(common_ridge$lb,
                                  common_lasso$lb,
                                  common_eln$lb)),
       shared_ub = rowMeans(cbind(common_ridge$ub,
                                  common_lasso$ub,
                                  common_eln$ub))) %>%
  arrange(desc(shared_mean_hr)) %>%
  slice_head(n = 20) %>%
  ggplot(aes(x = forcats::fct_reorder(variable, shared_mean_hr),
             y = shared_mean_hr, col = variable)) + 
  geom_point() +
  geom_linerange(aes(ymin = shared_lb, ymax = shared_ub)) + 
  theme_bw() +
  theme(legend.position = "none") +
  labs(x = "Significant Predictor Variables", 
       y = "Average Hazard Ratio") +
  coord_flip()
```

#### Demographic and Clinical
```{r share_dem}
intersect(ridge_weight_dem$variable, intersect(lasso_weight_dem$variable, eln_weight_dem$variable))
```

#### Recipient
```{r share_rec}
intersect(ridge_weight_rec$variable, intersect(lasso_weight_rec$variable, eln_weight_rec$variable))
```

#### Candidate
```{r share_can}
intersect(ridge_weight_can$variable, intersect(lasso_weight_can$variable, eln_weight_can$variable))
```

#### Donor
```{r share_don}
intersect(ridge_weight_don$variable, intersect(lasso_weight_don$variable, eln_weight_don$variable))
```

#### Procedural
```{r share_proc}
intersect(ridge_weight_proc$variable, intersect(lasso_weight_proc$variable, eln_weight_proc$variable))
```

### Shared Across ML {.tabset}

#### Top 20 Strongest Overall
```{r}
all_boost <- create_weight_table("gbmboost", elizabeth_vars$variable) %>%
  filter(lb > 0 | ub < 0) 
all_xgbl <- create_weight_table("xgbl", elizabeth_vars$variable) %>%
  filter(lb > 0 | ub < 0) 
all_xgbt <- create_weight_table("eln", elizabeth_vars$variable) %>%
  filter(lb > 0 | ub < 0) 
all_rfsrc <- create_weight_table("rfsrc", elizabeth_vars$variable) %>%
  filter(lb > 0 | ub < 0) 

shared_vars <- Reduce(intersect, list(all_boost$variable,
                                      all_xgbl$variable,
                                      all_xgbt$variable,
                                      all_rfsrc$variable))
  
common_boost <- all_boost %>%
  filter(variable %in% shared_vars)
common_xgbl <- all_xgbl %>%
  filter(variable %in% shared_vars)
common_xgbt <- all_xgbt %>%
  filter(variable %in% shared_vars)
common_rfsrc <- all_rfsrc %>%
  filter(variable %in% shared_vars)
  
tibble(variable = common_boost$variable,
       shared_mean_weight = rowMeans(cbind(common_boost$mean_weight,
                                           common_xgbl$mean_weight,
                                           common_xgbt$mean_weight,
                                           common_rfsrc$mean_weight))) %>%
  arrange(desc(shared_mean_weight)) %>%
  slice_head(n = 20) %>%
  ggplot(aes(x = forcats::fct_reorder(variable, shared_mean_weight),
             y = shared_mean_weight, fill = variable)) + 
  geom_col() +
  theme_bw() +
  theme(legend.position = "none") +
  labs(x = "Significant Predictor Variables", 
       y = "Average Importance") +
  coord_flip()
```

#### Demographic and Clinical
```{r share2_dem}
intersect(gbm_weight_dem$variable, 
          intersect(xgbt_weight_dem$variable,
                    intersect(xgbl_weight_dem$variable, rfsrc_weight_dem$variable)))
```

#### Recipient
```{r share2_rec}
intersect(gbm_weight_rec$variable, 
          intersect(xgbt_weight_rec$variable,
                    intersect(xgbl_weight_rec$variable, rfsrc_weight_rec$variable)))
```

#### Candidate
```{r share2_can}
intersect(gbm_weight_can$variable, 
          intersect(xgbt_weight_can$variable,
                    intersect(xgbl_weight_can$variable, rfsrc_weight_can$variable)))
```

#### Donor
```{r share2_don}
intersect(gbm_weight_don$variable, 
          intersect(xgbt_weight_don$variable,
                    intersect(xgbl_weight_don$variable, rfsrc_weight_don$variable)))
```

#### Procedural
```{r share2_proc}
intersect(gbm_weight_proc$variable, 
          intersect(xgbt_weight_proc$variable,
                    intersect(xgbl_weight_proc$variable, rfsrc_weight_proc$variable)))
```

