---
title: "Visualizing Survival ML Performance"
author: "Lathan Liou"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
      keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(fs)
library(cowplot)
library(ggridges)
library(forcats)
library(patchwork)
all_files <- list.files(path = "results_new",
                        full.names = TRUE,
                        pattern = "*.csv")
all_res <- all_files %>%
  map(~read_csv(.) %>%
        janitor::clean_names()) %>%
  setNames(all_files %>% 
             str_replace(".csv", "") %>%
             str_replace("results_new/", ""))

# modify rfsrc df to fit the others, since I had to use a reduced input set of vars
# full_vars = data.frame(variable = all_res$cox_1_featsel_$variable)
# new_rfsrc_featsel <- left_join(full_vars, all_res$rfsrc_1_featsel_,
#                                by = "variable")
# all_res$rfsrc_1_featsel_ <- new_rfsrc_featsel
```

## Comparing Short-Term and Long-Term C-Index
We may observe a higher C-index in shorter time-to-event cases. To roughly see this, we compare the cross-validated C-index of an SRTR cohort including patients who received transplants on an index date of 1-1-2011 with unaltered follow-up time with that of the same cohort of patients artificially censored after 2 years of follow-up.

```{r, warning=FALSE, message=FALSE, eval=FALSE}
make_perf_df <- function(start) {
  # retrieve all perf indices
  ind <- str_which(names(start), "_perf_")
  ci_wide <- map_dfc(ind, function(ind) start %>% pluck(ind) %>% select(-variable))
  ci_long <- ci_wide %>%
    pivot_longer(everything(),
                 names_to = "model",
                 values_to = "cindex")
  ci_long
}

test_files <- list.files(path = "results_test",
                         full.names = TRUE,
                         pattern = "*.csv")
test_res <- test_files %>%
  map(~read_csv(.) %>%
        janitor::clean_names()) %>%
  setNames(test_files %>% 
             str_replace(".csv", "") %>%
             str_replace("results_test/", ""))

make_perf_df(test_res) %>%
  mutate(model = case_when(
    model == "cox_ph_scale...1" ~ "Long-Term",
    model == "cox_ph_scale...2" ~ "Short-Term"
  )) %>%
  group_by(model) %>%
  dplyr::summarize(mean_cindex = mean(cindex, na.rm = TRUE),
                   sd_cindex = sd(cindex, na.rm = TRUE),
                   lb_cindex = quantile(cindex, probs = 0.025, na.rm = TRUE),
                   ub_cindex = quantile(cindex, probs = 0.975, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(mean_cindex))
```

## C-indices

```{r prep_perf_df}
make_perf_df <- function(start) {
  # retrieve all perf indices
  ind <- str_which(names(start), "_perf_")
  ci_wide <- map_dfc(ind, function(ind) all_res %>% pluck(ind) %>% select(-x1))
  ci_long <- ci_wide %>%
    pivot_longer(everything(),
                 names_to = "model",
                 values_to = "cindex")
  ci_long
}
perf_df <- make_perf_df(all_res)
perf_df$model <- recode(perf_df$model,
                        rfsrc_scale = "Random Survival Forests",
                        xgb_tree_scale = "XGBoost Tree",
                        ridge_scale = "Ridge",
                        cox_boost_scale = "Cox Boost",
                        xgb_linear_scale = "XGBoost Linear",
                        elastic_net_scale = "Elastic Net",
                        lasso_scale = "Lasso",
                        cox_ph_scale = "CoxPH")
```

### Table
```{r perf_tbl}
perf_df %>%
  group_by(model) %>%
  dplyr::summarize(mean_cindex = mean(cindex, na.rm = TRUE),
                   sd_cindex = sd(cindex, na.rm = TRUE),
                   lb_cindex = quantile(cindex, probs = 0.025, na.rm = TRUE),
                   ub_cindex = quantile(cindex, probs = 0.975, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(mean_cindex))
```

### Violin Plot
```{r model_comp_violin}
perf_df %>%
  mutate(model = fct_relevel(model,
                             "CoxPH",
                             "Ridge",
                             "Lasso",
                             "Elastic Net",
                             "Cox Boost",
                             "XGBoost Linear",
                             "XGBoost Tree",
                             "Random Survival Forests")) %>%
  ggplot(aes(x = model, y = cindex, fill = model)) + 
  geom_violin(alpha = 0.5) +
  geom_point(alpha = 0.5) +
  stat_summary(fun = "mean",
               geom = "crossbar", 
               width = 0.3,
               colour = "black") +
  theme_bw() +
  labs(x = "Model",
       y = "C-index",
       fill = "Model") + 
  coord_flip() + 
  scale_x_discrete(limits = rev) +
  annotate("rect", xmin = 4.5, xmax = 7.5,
           ymin = 0.69, ymax = 0.7) +
  annotate("text",
           x = 6,
           y = 0.695,
           col = "white",
           label = "Penalized",
           angle = 90) +
  annotate("rect", xmin = 1.7, xmax = 4.3,
           ymin = 0.69, ymax = 0.7) +
  annotate("text",
           x = 3,
           y = 0.695,
           col = "white",
           label = "Boost",
           angle = 90) +
  annotate("rect", xmin = 0.5, xmax = 1.5,
           ymin = 0.69, ymax = 0.7) +
  annotate("text",
           x = 1,
           y = 0.695,
           col = "white",
           label = "Tree",
           angle = 90)

```

## Features

### Selected Features Heatmap
```{r featsel_heatmap_rec, include = FALSE, fig.width = 8, fig.height = 12}
get_feat_selections <- function(start) {
  ind <- str_which(names(start), "_featsel_(?!aggr_)")
  feat_wide <- map_dfc(ind, ~ all_res %>% 
                         pluck(.x) %>% 
                         pivot_longer(-c(x1, total),
                                      names_to = "iter",
                                      values_to = "weight") %>%
                         group_by(x1) %>%
                         dplyr::summarize("{names(all_res)[[.x]]}" := sum(weight != 0, na.rm = TRUE)) %>%
                         ungroup() %>%
                         column_to_rownames(var = "x1"))
  feat_long <- feat_wide %>%
    rownames_to_column(var = "variable") %>%
    pivot_longer(-variable,
                 names_to = "model",
                 values_to = "n_selections")
  feat_long
}
feat_selections <- get_feat_selections(all_res)

feat_selections %>%
  mutate(model = case_when(
    model == "cox_1_featsel_" ~ "Cox",
    model == "eln_1_featsel_" ~ "Elastic Net",
    model == "gbmboost_1_featsel_" ~ "Cox Boost",
    model == "lasso_1_featsel_" ~ "Lasso",
    model == "rfsrc_1_featsel_" ~ "Random Survival Forests",
    model == "ridge_1_featsel_" ~ "Ridge",
    model == "xgbl_1_featsel_" ~ "XGBoost Linear",
    model == "xgbt_1_featsel_" ~ "XGBoost Tree"
  )) %>%
  filter(!model %in% c("Random Survival Forests", "Ridge", "XGBoost Linear"),
         str_detect(variable, "(?<![PRE])REC") | 
           str_detect(variable, "(?<![XCAN_])INSURANCE") |
           variable %in% c("MDRDeGFR_B", "VAD")) %>%
  filter(variable != "XCAN_MOST_RECENT_CREAT") %>%
  ggplot(aes(x = model, y = variable, fill = n_selections)) +
  geom_tile() + 
  geom_text(aes(label = n_selections), col = "black", size = 2) +
  scale_fill_gradient(low = "white", high = "blue") + 
  theme_bw() +
  labs(x = "Model",
       y = "Variable",
       fill = "Number of\nSelections") + 
  scale_y_discrete(limits = rev)
```

```{r featsel_heatmap_don, include = FALSE, fig.width = 8, fig.height = 12}
feat_selections %>%
  mutate(model = case_when(
    model == "cox_1_featsel_" ~ "Cox",
    model == "eln_1_featsel_" ~ "Elastic Net",
    model == "gbmboost_1_featsel_" ~ "Cox Boost",
    model == "lasso_1_featsel_" ~ "Lasso",
    model == "rfsrc_1_featsel_" ~ "Random Survival Forests",
    model == "ridge_1_featsel_" ~ "Ridge",
    model == "xgbl_1_featsel_" ~ "XGBoost Linear",
    model == "xgbt_1_featsel_" ~ "XGBoost Tree"
  )) %>%
  filter(!model %in% c("Random Survival Forests", "Ridge", "XGBoost Linear"),
         str_detect(variable, "DON_")) %>%
  ggplot(aes(x = model, y = variable, fill = n_selections)) +
  geom_tile() + 
  geom_text(aes(label = n_selections), col = "black", size = 2) +
  scale_fill_gradient(low = "white", high = "blue") + 
  theme_bw() +
  labs(x = "Model",
       y = "Variable",
       fill = "Number of\nSelections") + 
  scale_y_discrete(limits = rev)
```

```{r featsel_heatmap_can, include = FALSE, fig.width = 8, fig.height = 12}
feat_selections %>%
  mutate(model = case_when(
    model == "cox_1_featsel_" ~ "Cox",
    model == "eln_1_featsel_" ~ "Elastic Net",
    model == "gbmboost_1_featsel_" ~ "Cox Boost",
    model == "lasso_1_featsel_" ~ "Lasso",
    model == "rfsrc_1_featsel_" ~ "Random Survival Forests",
    model == "ridge_1_featsel_" ~ "Ridge",
    model == "xgbl_1_featsel_" ~ "XGBoost Linear",
    model == "xgbt_1_featsel_" ~ "XGBoost Tree"
  )) %>%
  filter(!model %in% c("Random Survival Forests", "Ridge", "XGBoost Linear"),
         str_detect(variable, "CARDIAC_ETIOLOGY") | 
           str_detect(variable, "CAN_RACE_SRTR") | 
           str_detect(variable, "XCAN_INSURANCE") |
           str_detect(variable, "XCAN") | variable %in% c("bmi_calculated", "Dialysis_Baseline", "DM_Baseline",
                                                         "PREV_MALIG", "WAIT_TIME",
                                                         "MDRDeGFR_WL")) %>%
  ggplot(aes(x = model, y = variable, fill = n_selections)) +
  geom_tile() + 
  geom_text(aes(label = n_selections), col = "black", size = 2) +
  scale_fill_gradient(low = "white", high = "blue") + 
  theme_bw() +
  labs(x = "Model",
       y = "Variable",
       fill = "Number of\nSelections") + 
  scale_y_discrete(limits = rev)
```

### Selected Features {.tabset}
```{r}
# filter out variables that were never selected by any method, excluding ridge
feat_sel_stats <- feat_selections %>%
  filter(!str_detect(model, "ridge")) %>%
  group_by(variable) %>%
  dplyr::summarize(avg_times = mean(n_selections, na.rm = TRUE),
                   tot_times = sum(n_selections, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(avg_times))
```

A selection of a feature is related to how important a model deemed it

#### All
```{r top_20_feat}
feat_sel_stats %>%
  slice(1:20) %>%
  mutate(avg_times = round(avg_times, 1),
         variable = recode(variable,
                           REC_POSTX_STROKE = "Post-transplant Stroke",
                           status_change = "Status Change",
                           REC_TOT_BILI = "Bilirubin",
                           REC_POSTX_DIAL = "Post-transplant Dialysis",
                           REC_IMMUNO_MAINT_MEDS = "Immunosuppresion",
                           REC_GRAFT_STAT = "Received Graft",
                           DM_Baseline = "Diabetes",
                           CAN_BMI = "Waitlist BMI",
                           CARDIAC_ETIOLOGY3 = "Ischemic Cardiomyopathy",
                           REC_CARDIAC_OUTPUT = "Cardiac Output",
                           REC_POSTX_AIRWAY = "Post-transplant Airway Dehiscence",
                           REC_AGE_AT_TX = "Age",
                           REC_FUNCTIONAL_STATUS4 = "Unclear Functional Status",
                           DON_AGE = "Donor Age",
                           REC_BMI = "BMI",
                           REC_LIFE_SUPPORT_TY0 = "No Life Support",
                           CAN_HGT_CM = "Waitlist Height",
                           REC_ACUTE_REJ_EPISODE2 = "Acute Rejection",
                           DON_BMI = "Donor BMI",
                           REC_POSTX_LOS = "Post-transplant LOS")) %>%
  ggplot(aes(x = forcats::fct_reorder(variable, avg_times),
             y = avg_times)) + 
  geom_col() +
  geom_text(aes(label = avg_times), hjust = 1, col = "white") +
  coord_flip() + 
  theme_bw() + 
  labs(x = "Variable",
       y = "Average number of times selected across all models")
```

```{r top_20_feat_indiv}
get_feat_sel_by_model <- function(feat_sel,
                                  .model,
                                  plot_title) {
  var_df <- feat_sel %>%
    filter(!str_detect(model, "cox"),
           !str_detect(model, "ridge"),
           str_detect(model, .model)) %>%
    arrange(desc(n_selections))
  
  ggplot(var_df %>%
           slice(1:20),
         aes(x = forcats::fct_reorder(variable, n_selections),
             y = n_selections)) + 
    geom_col() +
    coord_flip() + 
    theme_bw() + 
    labs(x = "Variable",
         y = "Number of times selected",
         title = plot_title)
}
feat_sel_tibble <- tibble(model_regex = c("lasso",
                                          "eln",
                                          "gbmboost"),
                          model = c("Lasso",
                                    "Elastic Net",
                                    "Cox Boost"))
individual_featsel_plots <- map2(feat_sel_tibble$model_regex,
                                 feat_sel_tibble$model,
                                 ~get_feat_sel_by_model(feat_selections,
                                                        .x, .y))
```

#### Lasso
```{r featsel_lasso}
p1 <- individual_featsel_plots[[1]] +
  geom_text(aes(label = n_selections), hjust = 1, col = "white")
p1
```

#### Elastic Net
```{r featsel_eln}
p2 <- individual_featsel_plots[[2]] +
  geom_text(aes(label = n_selections), hjust = 1, col = "white") 
p2
```

#### Cox Boost
```{r featsel_boost}
p3 <- individual_featsel_plots[[3]] + 
  geom_text(aes(label = n_selections), hjust = 1, col = "white")
p3
```

#### Cowplot of Feature Selection
```{r grid_featsel, include = FALSE, fig.width = 10, fig.height = 9}
(p1 + p2) / (p3 + plot_spacer())
```

### Direction of features {.tabset}

Weights of 0 not plotted in these graphs.

```{r}
get_feat_magnitude <- function(start) {
  ind <- str_which(names(start), "_featsel_(?!aggr_)")
  feat_wide <- map(ind, ~ all_res %>% 
                     pluck(.x) %>% 
                     pivot_longer(-x1,
                                  names_to = "iter",
                                  values_to = "weight") %>%
                     select(-iter) %>%
                     mutate(id = row_number()) %>%
                     rename("{names(all_res)[[.x]]}" := "weight")) %>%
    reduce(left_join, by = c("x1",
                             "id")) %>%
    rename(variable = x1)
}

feat_magnitude <- get_feat_magnitude(all_res)

feat_magnitude_long <- feat_magnitude %>%
  pivot_longer(-c(variable, id),
               names_to = "method",
               values_to = "weight") %>%
  mutate(method = str_replace(method, "_1_featsel_", ""))
```

#### Ridge

```{r ridge_rec}
feat_magnitude_long %>%
  filter(method == "ridge",
         weight != 0,
         str_detect(variable, "(?<![PRE])REC") | 
           str_detect(variable, "(?<![XCAN_])INSURANCE") |
           variable %in% c("MDRDeGFR_B", "VAD")) %>%
    filter(variable != "XCAN_MOST_RECENT_CREAT") %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  theme_bw() + 
  xlim(-0.5, 0.5) + 
  labs(x = "Weight",
       y = "Variable",
       title = "Recipient Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r ridge_can}
feat_magnitude_long %>%
  filter(method == "ridge",
         weight != 0,
         str_detect(variable, "CARDIAC_ETIOLOGY") | 
           str_detect(variable, "CAN_RACE_SRTR") | 
           str_detect(variable, "XCAN_INSURANCE") |
           str_detect(variable, "XCAN") | variable %in% c("bmi_calculated", "Dialysis_Baseline", "DM_Baseline",
                                                         "PREV_MALIG", "WAIT_TIME",
                                                         "MDRDeGFR_WL")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Candidate Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r ridge_don}
feat_magnitude_long %>%
  filter(method == "ridge",
         weight != 0,
         str_detect(variable, "DON_")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Donor Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

#### Lasso

```{r lasso_rec}
feat_magnitude_long %>%
  filter(method == "lasso",
         weight != 0,
         str_detect(variable, "(?<![PRE])REC") | 
           str_detect(variable, "(?<![XCAN_])INSURANCE") |
           variable %in% c("MDRDeGFR_B", "VAD")) %>%
    filter(variable != "XCAN_MOST_RECENT_CREAT") %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  xlim(-0.5, 0.5) + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Recipient Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r lasso_can}
feat_magnitude_long %>%
  filter(method == "lasso",
         weight != 0,
         str_detect(variable, "CARDIAC_ETIOLOGY") | 
           str_detect(variable, "CAN_RACE_SRTR") | 
           str_detect(variable, "XCAN_INSURANCE") |
           str_detect(variable, "XCAN") | variable %in% c("bmi_calculated", "Dialysis_Baseline", "DM_Baseline",
                                                         "PREV_MALIG", "WAIT_TIME",
                                                         "MDRDeGFR_WL")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Candidate Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r lasso_don}
feat_magnitude_long %>%
  filter(method == "lasso",
         weight != 0,
         str_detect(variable, "DON_")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Donor Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

#### Elastic Net

```{r eln_rec}
feat_magnitude_long %>%
  filter(method == "eln",
         weight != 0,
         str_detect(variable, "(?<![PRE])REC") | 
           str_detect(variable, "(?<![XCAN_])INSURANCE") |
           variable %in% c("MDRDeGFR_B", "VAD")) %>%
    filter(variable != "XCAN_MOST_RECENT_CREAT") %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  xlim(-0.3, 0.5) + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Recipient Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r eln_can}
feat_magnitude_long %>%
  filter(method == "eln",
         weight != 0,
         str_detect(variable, "CARDIAC_ETIOLOGY") | 
           str_detect(variable, "CAN_RACE_SRTR") | 
           str_detect(variable, "XCAN_INSURANCE") |
           str_detect(variable, "XCAN") | variable %in% c("bmi_calculated", "Dialysis_Baseline", "DM_Baseline",
                                                         "PREV_MALIG", "WAIT_TIME",
                                                         "MDRDeGFR_WL")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Candidate Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r eln_don}
feat_magnitude_long %>%
  filter(method == "eln",
         weight != 0,
         str_detect(variable, "DON_")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Donor Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

#### Cox Boost
```{r boost_rec}
feat_magnitude_long %>%
  filter(method == "gbmboost",
         weight != 0,
         str_detect(variable, "(?<![PRE])REC") | 
           str_detect(variable, "(?<![XCAN_])INSURANCE") |
           variable %in% c("MDRDeGFR_B", "VAD")) %>%
    filter(variable != "XCAN_MOST_RECENT_CREAT") %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  xlim(-0.1, 1) + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Recipient Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r boost_can}
feat_magnitude_long %>%
  filter(method == "gbmboost",
         weight != 0,
         str_detect(variable, "CARDIAC_ETIOLOGY") | 
           str_detect(variable, "CAN_RACE_SRTR") | 
           str_detect(variable, "XCAN_INSURANCE") |
           str_detect(variable, "XCAN") | variable %in% c("bmi_calculated", "Dialysis_Baseline", "DM_Baseline",
                                                         "PREV_MALIG", "WAIT_TIME",
                                                         "MDRDeGFR_WL")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  xlim(-1, 20) + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Candidate Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r boost_don}
feat_magnitude_long %>%
  filter(method == "gbmboost",
         weight != 0,
         str_detect(variable, "DON_")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") + 
  xlim(-1, 25) + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Donor Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

#### XGBL
```{r xgbl_rec}
feat_magnitude_long %>%
  filter(method == "xgbl",
         weight != 0,
         str_detect(variable, "(?<![PRE])REC") | 
           str_detect(variable, "(?<![XCAN_])INSURANCE") |
           variable %in% c("MDRDeGFR_B", "VAD")) %>%
    filter(variable != "XCAN_MOST_RECENT_CREAT") %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  xlim(-0.05, 0.05) + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Recipient Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r xgbl_can}
feat_magnitude_long %>%
  filter(method == "xgbl",
         weight != 0,
         str_detect(variable, "CARDIAC_ETIOLOGY") | 
           str_detect(variable, "CAN_RACE_SRTR") | 
           str_detect(variable, "XCAN_INSURANCE") |
           str_detect(variable, "XCAN") | variable %in% c("bmi_calculated", "Dialysis_Baseline", "DM_Baseline",
                                                         "PREV_MALIG", "WAIT_TIME",
                                                         "MDRDeGFR_WL")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Candidate Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r xgbl_don}
feat_magnitude_long %>%
  filter(method == "xgbl",
         weight != 0,
         str_detect(variable, "DON_")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Donor Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

#### XGBoost Tree
```{r xgbt_rec}
feat_magnitude_long %>%
  filter(method == "xgbt",
         weight != 0,
         str_detect(variable, "(?<![PRE])REC") | 
           str_detect(variable, "(?<![XCAN_])INSURANCE") |
           variable %in% c("MDRDeGFR_B", "VAD")) %>%
    filter(variable != "XCAN_MOST_RECENT_CREAT") %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  xlim(-0.01, 0.2) + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Recipient Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r xgbt_can}
feat_magnitude_long %>%
  filter(method == "xgbt",
         weight != 0,
         str_detect(variable, "CARDIAC_ETIOLOGY") | 
           str_detect(variable, "CAN_RACE_SRTR") | 
           str_detect(variable, "XCAN_INSURANCE") |
           str_detect(variable, "XCAN") | variable %in% c("bmi_calculated", "Dialysis_Baseline", "DM_Baseline",
                                                         "PREV_MALIG", "WAIT_TIME",
                                                         "MDRDeGFR_WL")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  theme_bw() + 
  xlim(-0.01, 0.05) + 
  labs(x = "Weight",
       y = "Variable",
       title = "Candidate Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r xgbt_don}
feat_magnitude_long %>%
  filter(method == "xgbt",
         weight != 0,
         str_detect(variable, "DON_")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") + 
  xlim(-0.01, 0.1) + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Donor Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

#### RSF
```{r rfsrc_rec}
feat_magnitude_long %>%
  filter(method == "rfsrc",
         weight != 0,
         str_detect(variable, "(?<![PRE])REC") | 
           str_detect(variable, "(?<![XCAN_])INSURANCE") |
           variable %in% c("MDRDeGFR_B", "VAD")) %>%
    filter(variable != "XCAN_MOST_RECENT_CREAT") %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  xlim(-0.01, 0.5) + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Recipient Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r rfsrc_can}
feat_magnitude_long %>%
  filter(method == "rfsrc",
         weight != 0,
         str_detect(variable, "CARDIAC_ETIOLOGY") | 
           str_detect(variable, "CAN_RACE_SRTR") | 
           str_detect(variable, "XCAN_INSURANCE") |
           str_detect(variable, "XCAN") | variable %in% c("bmi_calculated", "Dialysis_Baseline", "DM_Baseline",
                                                         "PREV_MALIG", "WAIT_TIME",
                                                         "MDRDeGFR_WL")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") +
  xlim(-0.01, 0.1) + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Candidate Characteristics") + 
  theme(axis.text = element_text(size = 5))
```

```{r rfsrc_don}
feat_magnitude_long %>%
  filter(method == "rfsrc",
         weight != 0,
         str_detect(variable, "DON_")) %>%
  ggplot(aes(x = weight,
             y = reorder(variable, desc(variable)))) + 
  # geom_point(alpha = 0.3) +
  geom_density_ridges() +
  geom_vline(xintercept = 0, col = "red") + 
  xlim(-0.01, 0.1) + 
  theme_bw() + 
  labs(x = "Weight",
       y = "Variable",
       title = "Donor Characteristics") + 
  theme(axis.text = element_text(size = 5))
```